---
title: "Lab 6 Report"
author: "Alejandro Garcia and Ramon Laborda"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is the report made in vignette for lab 6 of Advanced R programming. The content is of this lab has been.

- Brute force knapsack problem
- Dynamic approach knapsack problem
- Greedy approach knapsack problem
- Test creation for dynamic approach
- Optimization of approaches

## Knapsack problem

The knapsack problem or rucksack problem is a problem in combinatorial optimization: Given a set of items, each with a weight and a value, determine the number of each item to include in a collection so that the total weight is less than or equal to a given limit and the total value is as large as possible. It derives its name from the problem faced by someone who is constrained by a fixed-size knapsack and must fill it with the most valuable items.

Reference: https://en.wikipedia.org/wiki/Knapsack_problem

## Tests

To evaluate the functions implemented during this project, the following object has been created with the seed 42.

```{r eval=FALSE}
set.seed(42)
n <- 2000
knapsack_objects <- data.frame(
  w=sample(1:4000, size = n, replace = TRUE),
  v=runif(n = n, 0, 10000)
)
```

## Brute force solution

The knapsack problem has a lot of approaches to be solved, the only solution that is guaranteed to give a correct answer in all situations for the knapsack problem
is using brute-force search, i.e. going through all possible alternatives and return the maximum value found. This approach is of complexity $O(2n)$ since all possible combinations 2n needs to be evaluated.

The function implemented need of two parameters:

- x which is a data.frame with:
    - w weights of items
    - v values of items
- W maximum value of weight

It is possible to run the function with the following:

```{r eval=FALSE}
brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500)
```

This example takes 0.05 seconds to execute.

## Brute force parallel solution

In order to execute the function faster, we have implemented a parallel version of the brute force algorithm, to use it is that simple as put a parallel = TRUE in the function variable.

```{r eval=FALSE}
brute_force_knapsack_parallel(x = knapsack_objects[1:16,], W = 3500, parallel = TRUE)
```

## Dynamic algorithm solution

Another approach for the solution of the knapsack problem is with dynamic programming. It can solve the problem in pseudo-polynomial time so it is of complexity $O(nW)$. This function has the same parameters as the brute force.

```{r eval=FALSE}
knapsack_dynamic(x = knapsack_objects[1:16,], W = 3500)
```


## Greedy algorithm solution

The greedy solution is the most efficient one, specially with large number of items. The complexity of this algorithm is of $O(nlog(n))$, so is the fastest one of the three. This function has the same parameters as the brute force.


```{r eval=FALSE}
greedy_knapsack(x = knapsack_objects[1:16,], W = 3500)
```

There is also an improved version of the greedy algorithm where it is possible to get a better solution with a little bit more of time.

```{r eval=FALSE}
greedy_knapsack_improved(x = knapsack_objects[1:16,], W = 3500)
```

## Benchmark

In order to see how these functions work, we evaluated them with a benchmark.

```{r eval = FALSE}
library(microbenchmark)
set.seed(42)
n <- 2000
knapsack_objects <- data.frame(
  w=sample(1:4000, size = n, replace = TRUE),
  v=runif(n = n, 0, 10000)
)



microbenchmark(
  "Brute Normal" = brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500),
  "Dynamic" = knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500),
  "Greedy" = greedy_knapsack(x = knapsack_objects[1:1000000,], W = 3500),
  times = 1
)


Unit: milliseconds
         expr        min         lq       mean     median         uq        max neval
 Brute Normal   13.14186   13.14186   13.14186   13.14186   13.14186   13.14186     1
      Dynamic 6488.38793 6488.38793 6488.38793 6488.38793 6488.38793 6488.38793     1
       Greedy 1208.93595 1208.93595 1208.93595 1208.93595 1208.93595 1208.93595     1



````   

